Supplementary Material for \emph{A Guide to Pre-processing High-Frequency Animal Tracking Data}

### 2020-12-15 docs/supplementary_material.tex
add edit to tex file
add even more final pdfs

            pdftitle={Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data},
            pdfauthor={Pratik R. Gupte; Christine E. Beardsworth; Orr Spiegel; Emmanuel Lourie; Allert I. Bijleveld},

@@

\title{Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data}
\author{Pratik R. Gupte \and Christine E. Beardsworth \and Orr Spiegel \and Emmanuel Lourie \and Allert I. Bijleveld}
\date{2020-12-03}

@@

\hypertarget{processing-egyptian-fruit-bat-tracks}{%
\chapter{Processing Egyptian fruit bat tracks}\label{processing-egyptian-fruit-bat-tracks}}

>>>>

            pdftitle={Supplementary Material for A Guide to Pre-processing High-Frequency Animal Tracking Data},
            pdfauthor={Pratik R. Gupte; Christine E. Beardsworth; Orr Spiegel; Emmanuel Lourie; Sivan Toledo; Ran Nathan; Allert I. Bijleveld},

@@

\title{Supplementary Material for \emph{A Guide to Pre-processing High-Frequency Animal Tracking Data}}
\author{Pratik R. Gupte \and Christine E. Beardsworth \and Orr Spiegel \and Emmanuel Lourie \and Sivan Toledo \and Ran Nathan \and Allert I. Bijleveld}
\date{2020-12-15}

@@

\hypertarget{processing-egyptian-fruit-bat-tracks}{%
\chapter{Processing Egyptian Fruit Bat Tracks}\label{processing-egyptian-fruit-bat-tracks}}
